### 2021-01-28 ch03_esmvaltool/esmvaltool.tex
Adapted copyright statements
Added recipe for Meehl et al. (2020) to chapter 03

\begin{figure}[t]
  \centering
  \includegraphics[width=\LargeFigureWidth{}]{
    ch03_esmvaltool/figs/esmvaltool_schematic.pdf}
  \caption{Schematic representation of the \acf{ESMValTool}. First, input data
    is preprocessed by the \acf{ESMValCore}. Second, the preprocessed data is
    read by diagnostic scripts, which create the final output (\eg{} plots).
    The user can specify the desired input datasets, preprocessing operations
    and diagnostic scripts in the recipe, which is a configuration file that
    controls the main workflow of the \acs{ESMValTool}. Taken and modified from
    \textcite{Righi2020}.}
  \label{fig:03:esmvaltool_schematic}
\end{figure}

@@

\begin{table}[!b]
  \centering
  \begin{tabulary}{\columnwidth}{L L L}
    \toprule
    Type & Name & Main reference \\
    \midrule
    Recipe & \emph{bock20jgr} (figures 8 and 10) & \autocite{Bock2020} \\
    & \emph{cox18nature} & \autocite{Cox2018} \\
    & \emph{ecs} & \autocite{Gregory2004} \\
    & \emph{flato13ipcc} (figure 9.42) & \autocite{Flato2013} \\
    & \emph{schlund20esd} & \autocite{Schlund2020a} \\
    & \emph{schlund20jgr\_gpp\_abs\_rcp85} & \autocite{Schlund2020} \\
    & \emph{schlund20jgr\_gpp\_change\_1pct} & \autocite{Schlund2020} \\
    & \emph{schlund20jgr\_gpp\_change\_rcp85} & \autocite{Schlund2020} \\
    & \emph{tcr} & \autocite{Gregory2008} \\
    \midrule
    \ac{CMOR}izer & CRU & \autocite{Harris2014} \\
    & CT2019 & \autocite{Jacobson2020} \\
    & GCP & \autocite{Friedlingstein2020} \\
    & HWSD & \autocite{Wieder2014} \\
    & JMA-TRANSCOM & \autocite{Maki2010} \\
    & LAI3g & \autocite{Zhu2013} \\
    & LandFlux-EVAL & \autocite{Mueller2013} \\
    & MLS-Aura & \autocite{Read2015} \\
    & MTE & \autocite{Jung2011} \\
    & NDP & \autocite{Gibbs2006} \\
    & Scripps-\ac{CO2} & \autocite{Keeling2005} \\
    \bottomrule
  \end{tabulary}
  \caption{Summary of new recipes and \acs{CMOR}ization scripts for
    observational data contributed to the \acf{ESMValTool} by the author of
    this thesis. The corresponding file names of the recipes in the
    \acs{ESMValTool} repository are given by
    \emph{recipe\_(name\_in\_table).yml}.}
  \label{tab:03:changes_to_esmvaltool}
\end{table}

@@

In addition to the ported recipes, several new recipes and diagnostic scripts
have been contributed to the public \ac{ESMValTool} repository (see
\cref{tab:03:changes_to_esmvaltool} for a summary). Some of these include the
analyses performed in other chapters of this thesis, namely
\emph{recipe\_bock20jgr.yml} (\cref{ch:04:papers_ecs_tcr_assessment}),
\emph{recipe\_schlund20esd.yml} (\cref{ch:05:paper_ecs}) and
\emph{recipe\_schlund20jgr\_*.yml} (\cref{ch:06:paper_gpp}).
\emph{recipe\_ecs.yml} and \emph{recipe\_tcr.yml} contain diagnostic scripts
that are able to calculate the climate metrics \ac{ECS} and \ac{TCR} for
arbitrary model output (see \cref{sec:02:climate_sensitivity}). Corresponding
plots are shown in \cref{fig:02:gregory_regression,fig:02:tcr}.
\emph{recipe\_cox18nature.yml} reproduces the analysis of \textcite{Cox2018},
who introduce an emergent constraint in \ac{ECS} based on a global temperature
variability metric $\Psi$. \Cref{fig:03:cox18:a} shows $\Psi$ over the past 85
years for \acs{CMIP}5 models and observations form HadCRUT4
\autocite{Morice2012}. Since high sensitivity climate models exhibit higher
values of $\Psi$ than low sensitivity models, an emergent relationship between
\ac{ECS} and $\Psi$ can be established (\cref{fig:03:cox18:b}). With
observations of $\Psi$, \ac{ECS} can eventually be constrained to $\left( 2.8
\pm 0.6 \right) \unit{K}$ ($66 \unit{\%}$ confidence range). More details on
this including the calculation of $\Psi$ are given in \cref{subsec:05:cox}.

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=\LargeFigureWidth{}]{
    ch03_esmvaltool/figs/esmvaltool_schematic.pdf}
  \caption{Schematic representation of the \acf{ESMValTool}. First, input data
    is preprocessed by the \acf{ESMValCore}. Second, the preprocessed data is
    read by diagnostic scripts, which create the final output (\eg{} plots).
    The user can specify the desired input datasets, preprocessing operations
    and diagnostic scripts in the recipe, which is a configuration file that
    controls the main workflow of the \acs{ESMValTool}.
    \AdaptedFrom{Righi2020}.}
  \label{fig:03:esmvaltool_schematic}
\end{figure}

@@

\begin{table}[!b]
  \centering
  \begin{tabulary}{\columnwidth}{L L L}
    \toprule
    Type & Name & Main reference \\
    \midrule
    Recipe & \emph{bock20jgr} (figures 8 and 10) & \autocite{Bock2020} \\
    & \emph{cox18nature} & \autocite{Cox2018} \\
    & \emph{ecs} & \autocite{Gregory2004} \\
    & \emph{flato13ipcc} (figure 9.42) & \autocite{Flato2013} \\
    & \emph{meehl20sciadv} & \autocite{Meehl2020} \\
    & \emph{schlund20esd} & \autocite{Schlund2020a} \\
    & \emph{schlund20jgr\_gpp\_abs\_rcp85} & \autocite{Schlund2020} \\
    & \emph{schlund20jgr\_gpp\_change\_1pct} & \autocite{Schlund2020} \\
    & \emph{schlund20jgr\_gpp\_change\_rcp85} & \autocite{Schlund2020} \\
    & \emph{tcr} & \autocite{Gregory2008} \\
    \midrule
    \ac{CMOR}izer & CRU & \autocite{Harris2014} \\
    & CT2019 & \autocite{Jacobson2020} \\
    & GCP & \autocite{Friedlingstein2020} \\
    & HWSD & \autocite{Wieder2014} \\
    & JMA-TRANSCOM & \autocite{Maki2010} \\
    & LAI3g & \autocite{Zhu2013} \\
    & LandFlux-EVAL & \autocite{Mueller2013} \\
    & MLS-Aura & \autocite{Read2015} \\
    & MTE & \autocite{Jung2011} \\
    & NDP & \autocite{Gibbs2006} \\
    & Scripps-\ac{CO2} & \autocite{Keeling2005} \\
    \bottomrule
  \end{tabulary}
  \caption{Summary of new recipes and \acs{CMOR}ization scripts for
    observational data contributed to the \acf{ESMValTool} by the author of
    this thesis. The corresponding file names of the recipes in the
    \acs{ESMValTool} repository are given by
    \emph{recipe\_(name\_in\_table).yml}.}
  \label{tab:03:changes_to_esmvaltool}
\end{table}

@@

In addition to the ported recipes, several new recipes and diagnostic scripts
have been contributed to the public \ac{ESMValTool} repository (see
\cref{tab:03:changes_to_esmvaltool} for a summary). Some of these include the
analyses performed in other chapters of this thesis, namely
\emph{recipe\_bock20jgr.yml} (\cref{ch:04:papers_ecs_tcr_assessment}),
\emph{recipe\_meehl20sciadv.yml} (\cref{ch:04:papers_ecs_tcr_assessment}),
\emph{recipe\_schlund20esd.yml} (\cref{ch:05:paper_ecs}) and
\emph{recipe\_schlund20jgr\_*.yml} (\cref{ch:06:paper_gpp}).
\emph{recipe\_ecs.yml} and \emph{recipe\_tcr.yml} contain diagnostic scripts
that are able to calculate the climate metrics \ac{ECS} and \ac{TCR} for
arbitrary model output (see \cref{sec:02:climate_sensitivity}). Corresponding
plots are shown in \cref{fig:02:gregory_regression,fig:02:tcr}.
\emph{recipe\_cox18nature.yml} reproduces the analysis of \textcite{Cox2018},
who introduce an emergent constraint in \ac{ECS} based on a global temperature
variability metric $\Psi$. \Cref{fig:03:cox18:a} shows $\Psi$ over the past 85
years for \acs{CMIP}5 models and observations form HadCRUT4
\autocite{Morice2012}. Since high sensitivity climate models exhibit higher
values of $\Psi$ than low sensitivity models, an emergent relationship between
\ac{ECS} and $\Psi$ can be established (\cref{fig:03:cox18:b}). With
observations of $\Psi$, \ac{ECS} can eventually be constrained to $\left( 2.8
\pm 0.6 \right) \unit{K}$ ($66 \unit{\%}$ confidence range). More details on
this including the calculation of $\Psi$ are given in \cref{subsec:05:cox}.
